\songtitle{Come to me}
\begin{song}

I am the Lord, your God, \\
I go before you now. \\
I stand beside you, I'm all around you, \\
though you feel I'm far away. \\
I'm closer than your breath, \\
I am with you wherever you go.

I am the Lord, your Peace, \\
no evil will conquer you! \\
Steady now your heart and mind, \\
come into My rest. \\
Oh, let your faith arise, \\
lift up your weary head. \\
I am with you wherever you go.

\begin{chorus}
    Come to me, I'm all you need! \\
    Come to me, I'm everything! \\
    Come to me, I'm all you need! \\
    Come to me, I'm your everything!
\end{chorus}

I am your anchor, in the wind and the waves, \\
and I am your steadfast, so don't be afraid. \\
If your heart and flesh fail you, \\
I'm your faithful strength. \\
And I am with you wherever you go.

(Bridge) \\
When the storm rages, I won't be afraid, \\
'cause I have locked eyes on You face to face. \\
Your voice I will follow, \\
Your eyes I will see, \\
come a little closer, come close to me.

Oh, 'cause You are my anchor \\
in the wind and waves, \\
I will stand steadfast, oh, You are my ... \\
And I won't be afraid, \\
'cause even in the darkest nights, \\
I know You are there, \\
so I press into You, Jesus!

'Cause You are my anchor \\
in the wind and waves, \\
oh, and You are my steadfast \\
and I won't be afraid. \\
If my heart and flesh fail me, \\
You're my faithful strength, \\
You are with us wherever we go.

So Jesus, we come to You \\
'cause You're all we need! \\
And we come to You, our everything! \\
Oh, we come to You 'cause You're all we need! \\
And we come to You, our everything!
\end{song}
