\songtitle{O Mother of the Lord}
\begin{song}

\begin{chorus}
    O Mother of the Lord, our Lady and Queen. \\
    God shaped, within your womb, the maker of man. \\
    Trough you, Holy light has come to dwell among us, \\
    Mary, you are the joy of God, \\
    his chosen from all mankind.
\end{chorus}

Mary, full of grace, gladly we greet you. \\
On you has shone down the glory of the Lord. \\
Heaven has shower’d us with grace, \\
o Mary, pray for us: unfading Morning Star.

Mary, full of grace, Ark of the Promise. \\
From your womb has come the Son of God made flesh. \\
In you dwells our Emmanuel, o Mary, \\
pray for us: true temple of our Lord.

Mary, full of grace, Queen of the Heavens. \\
For our sake your bore the King of all the World. \\
Through you the Saviour is revealed, \\
o Mary, pray for us: beloved spouse of God.

Mary, full of grace, Purest of Virgins! \\
You have given life to Him who made us all. \\
In you the heavens come to earth; \\
o Mary, pray for us: our mother without stain.

Mary, full of grace, Refuge of Sinners. \\
God makes new in you the whole of humankind. \\
In you the Saviour made his home, \\
o Mary, pray for us: our new and sinless Eve.

Mary, full of grace, \\
God's humble servant generations praise and magnify your name. \\
The Holy Spirit came on you, o Mary, \\
pray for us: all ages call you blessed.

Mary, full of grace, Queen of the Angels. \\
With your Holy Son, you reign up on the earth. \\
Seated in splendour on your throne, \\
o Mary, pray for us: beloved of the saints.
\end{song}
